The problem and promise of scale in animal social multilayer networks

### 2020-02-10 paper/manuscript.Rmd
caribou loc section

## Caribou location data
We used GPS location data collected from Fogo Island caribou in 2017 and 2018.
Adult female caribou were immobilized and fitted with global positioning system
(GPS) collars (Lotek Wireless Inc., Newmarket, ON, Canada, GPS4400M collars,
1,250 g) as described by [@Schaefer_2013]. Collars were programmed to collect
location fixes every 2 hours. Prior to analyses, we subset GPS fixes into a
discrete removed all erroneous and outlier GPS fixes following
[@BJ_RNERAAS_2010]. We did not collar all female caribou in the herd; however,
we assumed that our sample of collared animals was random.

>>>>

## Caribou location data
We used GPS location data collected from Fogo Island caribou in 2017 and 2018.
Adult female caribou were immobilized and fitted with global positioning system
(GPS) collars (Lotek Wireless Inc., Newmarket, ON, Canada, GPS4400M collars,
1,250 g) as described by [@Schaefer_2013]. Collars were programmed to collect
location fixes every 2 hours. Prior to analyses, we subset GPS fixes into a
discrete removed all erroneous and outlier GPS fixes following
[@BJ_RNERAAS_2010] <!--TODO: fix this ref-->. We did not collar all female
caribou in the herd; however, the proportion of marked adult females was
approximately 15% and we assumed these individuals were randomly distributed
throughout the population.
